---
title: "group14wyw"
author: "me"
date: "2023-03-13"
output:
  pdf_document: default
  word_document: default
---
```{r packages, include=FALSE}
library(ggplot2)
library(readr)
library(dplyr)
library(tidyverse)
library(moderndive)
library(gapminder)
library(GGally)
library(psych)
library(jtools)
library(reshape2)
library(sjPlot)
library(stats)

```
# GLM Part 1

In this part, we read dataset14.csv, and cleansing was performed on the data. For instance, deleting rows with null values and converting A and B to 0 and 1
```{r dataset, include=FALSE}
coffee <- read.csv("dataset14.csv")
coffee$Qualityclass <- as.integer(as.factor(coffee$Qualityclass))-1
coffee_glm <- na.omit(coffee)
```

&nbsp;

## correlation analysing
```{r, eval = TRUE, fig.align = "center", fig.cap = "\\label{fig:scat} correlation between each variables", fig.pos = "H"}
ggpairs(coffee_glm[,2:8])
```

Figure 1 shows there is strong correlation between the first three variables: aroma, flavor and acidity. In addition, aroma, flavor and acidity have medium correlation with QualityClass, category is in weak correlation. However, the correlation of the last two cariables are strongly weak. 

The strong correlation shows that we need to do further data cleaning. First, seperating the dataset into two catagories, one callled coffee_cor, the other one is coffee_non_cor.

```{r, eval=TRUE, echo=FALSE}
coffee1_1 <- coffee_glm[,2:4]
coffee1_2 <- coffee_glm[,5:8]
coffee1_3 <- coffee_glm[,2:8]
```

## model 1 : The first three variables with principal component analysis and 3 variables.

We performed a principal components analysis on coffee1_1.
```{r, eval=TRUE, echo=FALSE}
coffee1_1_pca<-princomp(coffee1_1, cor=T)
summary(coffee1_1_pca)
```
As we can see from the table above, the cumulative proportion of the first component is 0.8746, so we can only choose the first component.
```{r, eval=TRUE, echo=FALSE}
cor11 <- cor(coffee1_1, coffee1_1)
pca11 <- principal(cor11, nfactor = 1, rotate= "cluster")
score11 <- predict.psych(pca11, coffee1_1 )
final_1 <- cbind(score11, coffee1_2)
```

&nbsp;

Trying: 1st glm function
```{r, eval=TRUE, echo=FALSE}
model_1 <- glm(Qualityclass ~ PC1+category_two_defects+
                 altitude_mean_meters+harvested, data = final_1, 
               family = binomial(link = "cloglog"))
summary(model_1)
```

&nbsp;

## model 2 : All variables with principal component analysis.

We performed a principal components analysis on coffee1_3.
```{r, eval=TRUE,echo=FALSE}
coffee1_3_pca<-princomp(coffee1_3, cor=T)
summary(coffee1_3_pca)
```
As we can see from the table above, the cumulative proportion of the fourth component is 0.8608002, so we can only choose the first four component.
```{r, eval=TRUE, echo=FALSE}
cor13 <- cor(coffee1_3[,1:6], coffee1_3[,1:6])
pca13 <- principal(cor13, nfactor = 4, rotate= "cluster")
score13 <- predict.psych(pca13, coffee1_3[,1:6] )
final_2 <- cbind(score13, coffee_glm$Qualityclass)
```

Trying: 2st glm function
```{r, eval=TRUE, echo=FALSE}
final_2 <- as.data.frame(final_2)
model_2 <- glm(V5 ~ RC1+RC2+RC4+RC3, data = final_2, 
               family = binomial(link = "logit"))
summary(model_2)
```

All of these two models do not fit well, and the correlation figure shows that the last three variables have really weak relationship with QualityClass, so in this model, we try to fit the third model by deleting harvested, category and altitude.

&nbsp;

## model 3 : First 3 variables with principal component analysis.
```{r, eval=TRUE, echo=FALSE}
coffee1_4 <- coffee1_3[,1:3]
coffee1_4_pca<-princomp(coffee1_4, cor=T)
summary(coffee1_4_pca)
```
As we can see from the table above, the cumulative proportion of the second component is 0.9561369, so we can only choose the first two components.
```{r, eval=TRUE,echo=FALSE}
cor14 <- cor(coffee1_4, coffee1_4)
pca14 <- principal(cor14, nfactor = 2, rotate= "cluster")
score14 <- predict.psych(pca14, coffee1_4)
final_3 <- cbind(score14, coffee_glm$Qualityclass)
```

Trying: 3rd glm function
```{r, eval=TRUE,echo=FALSE}
final_3 <- as.data.frame(final_3)
model_3 <- glm(V3 ~ RC1+RC2, data = final_3, 
               family = binomial(link = "logit"))
summary(model_3)
```
The p-values presented in the table above are all less than 0.05, indicating that the third model fits well and that the first three variables are the most important factors influencing the goodness of the fit.